### 2022-12-05 abstract.tex
table formatting

The first and largest part of this thesis consists of three extensions to a
recently proposed reverse-Bayes method for quantifying replication success. The
key idea of the method is to challenge the data from the original study with a
sceptical prior so that the resulting posterior no longer provides evidence for
the finding from the study. Replication success is then achieved if there is
conflict between the sceptical prior and the replication data. The procedure can
be summarized in a single quantitative measure, termed the sceptical $p$-value.
% extension 1
The first extension recalibrates the sceptical $p$-value to produce more
appropriate inferences in terms of effect size. The recalibration is chosen such
that for original studies which were borderline significant, replication success
can only be achieved if the effect estimate from the replication study is larger
than the effect estimate from the original study. We find that the recalibrated
sceptical $p$-value has good frequentist properties comparable to the standard
method used in practice.
% extension 2
The second extension replaces tail probabilities with Bayes factors as measures
of evidence. The procedure can again be summarized in a single measure called
the sceptical Bayes factor.
% The sceptical prior is now determined such that the original finding is no
% longer convincing in terms of a Bayes factor. In contrast to tail
% probabilities,
% We find that the extended method combines two notions of replicability: It
% requires that original and replication study independently provide evidence for
% an effect and ensures that their effect estimates are compatible.
The sceptical Bayes factor has similar properties as the sceptical $p$-value but
it avoids a statistical paradox which the sceptical $p$-value suffers from -- in
some situations the sceptical $p$-value may indicate replication success even
though the effect estimate from the replication is arbitrarily smaller than
effect estimate from the original study. % , which cannot happen with the sceptical
% Bayes factor.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
The third extension provides a framework for Bayesian design of replication
studies which allows for combining data from the original study with external
knowledge. This approach can lead to potentially more efficient designs compared
to classical approaches, and it can be used for replication design based on both
the sceptical $p$-value and the sceptical Bayes factor.
% External knowledge, such as data from other studies, is ubiquitous in the
% replication setting and taking it into account can lead to potentially more
% efficient designs compared to classical approaches.

The second part of this thesis also deals with reverse-Bayes methods, but with a
broader scope of applications than replication studies as in the first part. The
reverse-Bayes idea was first proposed in the 1950s, but it has mostly been
forgotten. To increase awareness and show potential use cases, reverse-Bayes
history and methods are summarized in a comprehensive review. The review
includes also some new results on connections between revere-Bayes methods and
meta-analysis. % Finally, a
% commentary paper on a recently proposed reverse-Bayes method draws connections
% to other reverse-Bayes methods.

The last part of this thesis revolves around research integrity issues in
methodological research. Questionable research practices, such as selective
reporting of results, are often seen as main cause for replicability issues in
the medical and social sciences. These practices can similarly harm
methodological research, but are often not recognized. To raise awareness, an
illustrative simulation study is conducted in which it is shown how a novel
method can easily be presented as superior over established competitor methods
if questionable research practices are employed.

>>>>

Possible answers to this question are given in the first and largest part of
this thesis. It consists of three extensions to a recently proposed
reverse-Bayes method for quantifying replication success. The key idea of the
method is to challenge the data from the original study with a sceptical prior
so that the resulting posterior distribution is no longer ``significant''. The
goal of the replication study is then to show that the sceptical prior is
unrealistic, and replication success is achieved if there is sufficient conflict
between the prior and the replication data. The procedure can be summarized in a
single quantitative measure, termed the sceptical $p$-value.
% extension 1
The first extension recalibrates the sceptical $p$-value to produce more
appropriate inferences in terms of effect size. The recalibration is chosen such
that for original studies which were borderline significant, replication success
can only be achieved if the effect estimate from the replication study is larger
than the effect estimate from the original study. We find that the recalibrated
sceptical $p$-value has good frequentist properties comparable to the standard
method used in practice.
% extension 2
The second extension replaces tail probabilities with Bayes factors as measures
of evidence. The procedure can again be summarized in a single measure called
the sceptical Bayes factor.
% The sceptical prior is now determined such that the original finding is no
% longer convincing in terms of a Bayes factor. In contrast to tail
% probabilities,
% We find that the extended method combines two notions of replicability: It
% requires that original and replication study independently provide evidence for
% an effect and ensures that their effect estimates are compatible.
The sceptical Bayes factor has similar properties as the sceptical $p$-value but
it avoids a statistical paradox which the sceptical $p$-value suffers from -- in
some situations the sceptical $p$-value may indicate replication success even
though the effect estimate from the replication is arbitrarily smaller than the
effect estimate from the original
study. % , which cannot happen with the sceptical
% Bayes factor.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
The third extension provides a framework for Bayesian design of replication
studies which allows for combining data from the original study with external
knowledge. This approach can lead to potentially more efficient designs compared
to classical approaches, and it can be used for replication design based on both
the sceptical $p$-value and the sceptical Bayes factor.
% External knowledge, such as data from other studies, is ubiquitous in the
% replication setting and taking it into account can lead to potentially more
% efficient designs compared to classical approaches.

The second part of this thesis also deals with reverse-Bayes methods, but with a
broader scope of applications than replication studies. The reverse-Bayes idea
was first proposed in the 1950s, but it has mostly been forgotten. To increase
awareness and show potential use cases, reverse-Bayes history and methods are
summarized in a comprehensive review. The review includes also some new results
on connections between reverse-Bayes methods and meta-analysis. % Finally, a
% commentary paper on a recently proposed reverse-Bayes method draws connections
% to other reverse-Bayes methods.

The last part of this thesis revolves around research integrity issues in
methodological research. Questionable research practices, such as selective
reporting of results, are often seen as main cause for replicability issues in
the medical and social sciences. These practices can similarly harm
methodological research, but are often not recognized. To raise awareness, an
illustrative simulation study is conducted in which it is shown how a novel
method can easily be presented as superior over established competitor methods
if questionable research practices are employed. Finally, several
recommendations are given to alleviate these issues, most importantly the need
for simulation protocols.
